The imprint of global magma oceans on exoplanet demographics

### 2023-01-06 src/tex/ms.tex
separate mission-specific and optimistic case

\begin{note}
   The fidelity of a future detection or falsification of a magma ocean signature will depend on the significance with which the null hypothesis can be excluded.
   As a consequence, instrumentation and survey strategy aiming at testing the hypothesis should aim at maximizing the probability of a true positive detection given the existence of the effect.
   This is called the \textit{statistical power}: the probability of correctly rejecting a false null hypothesis.
   Before turning to mission design trades that influence the statistical power in Sect.~\ref{sec:mission-design-trades}, we explore its behavior as a function of various free parameters of the magma ocean model.
    ...
\begin{figure*}[ht!]
%    \script{figurescript.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/example_statistical_power.pdf}
        \caption{
        Statistical power of the runaway greenhouse hypothesis test as a function of model parameters.
        }
        \label{fig:statistical_power}
    \end{centering}
\end{figure*}

@@

\subsection{Diagnostic power of upcoming exoplanet missions}\todo[inline]{PLATO: needed sample size, precision}

\subsection{Mission design trades}\label{sec:mission-design-trades}

>>>>

@@

\subsection{Diagnostic power of upcoming exoplanet missions}\todo[inline]{PLATO: needed sample size, precision}
The fidelity of a future detection or falsification of a magma ocean signature will depend on the significance with which the null hypothesis can be excluded.
As a consequence, instrumentation and survey strategy aiming at testing the hypothesis should aim at maximizing the probability of a true positive detection given the existence of the effect.
...

\subsection{Mission design trades}\label{sec:mission-design-trades}
We now turn to mission design trades that influence the statistical power for testing the runaway greenhouse hypothesis.
...
